---
title: "Attack Chase Death"
output: html_document
date: "2024-10-29"
---

```{r setup, include=FALSE}
## libraries ##
library(tidyverse)
library(ggplot2)
library(lmerTest)
library(doParallel)
library(parallel)
library(foreach)
library(here)
library(fs)
library(lmtest)
library(blme)
library(scales)
library(ggthemr)
library(RColorBrewer)
library(broom.mixed)
library(brms)

## hand written functions ##
source(path(here(), "R", 'mutate_cond.R'))
source(path(here(), "R", 'create_distance_df.R'))
source(path(here(), "R", 'clean_behavioral_data.R'))
source(path(here(), "R", 'compile_ieeg_csv_files.R'))
source(path(here(), "R", 'run_and_plot_lme_models.R'))
source(path(here(), "R", 'separate_mfg_sfg.R'))

## plotting helpers ##
ggthemr("light")
ghost_colors <- c("#E48DB7","#55BBC8", "#DE0D16")
getPalette = colorRampPalette(brewer.pal(17, "Set1"))

c25 <- c(
  "dodgerblue2", "#E31A1C", # red
  "green4",
  "#6A3D9A", # purple
  "#FF7F00", # orange
  "black", "gold1",
  "skyblue2", "#FB9A99", # lt pink
  "palegreen2",
  "#CAB2D6", # lt purple
  "#FDBF6F", # lt orange
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

```


## right MFG Figures and Analysis

Creates the figures and fits models for all of the right MFG Only analyses in the paper

It requires:
* `hfa_ieeg_dlpfc_all_subs_logged_iti_onset.csv` which is an output of `analyhsis/freq_power_analyses/compile_ieeg_files_iti_logged_trialonset.Rmd`
* `all_subs_complete_distance_df.csv` which is an output of `analysis/cleaning_ieeg_behavior/combine_ieeg_subs_behavior.Rmd`.
* `mni_coordinates_all_subs.csv` which is an output of `analysis/anatomical_plotting/create_mni_csv.Rmd`
* `SUBJECTID_attack_events.csv` files which are created by the individual subject cleaning scripts in `analysis/cleaning_ieeg_behavior/`

It produces:
* `figure5_chase_death_rmfg_plot.png` in the `figures/attack` folder.
* `attack_rmfg_hfa_trial_time_model_brms.RData` in the `results/attack` folder.




```{r load-data}

## HFA ##
dlpfc_hfa_data <- read_csv( path(here(), "munge", "hfa_ieeg_dlpfc_all_subs_logged_iti_onset.csv"))

# separate dlpfc into sfg and mfg
dlpfc_hfa_data <- dlpfc_hfa_data %>%
  mutate(electrode = gsub("_.*", "", electrode))
dlpfc_hfa_data <- separate_mfg_sfg(dlpfc_hfa_data)
sfg_hfa_data <- dlpfc_hfa_data %>% filter(sfg == 1) %>% select(-sfg, -mfg)
mfg_hfa_data <- dlpfc_hfa_data %>% filter(mfg == 1) %>% select(-sfg, -mfg)


# behavioral data #
all_subs_g_dist <- read_csv(path(here(), "munge", "all_subs_complete_distance_df.csv"))
all_subs_ng_dist <- read_csv(path(here(), "munge", "all_subs_noghost_complete_distance_df.csv"))


# add ITI to behavioral df
behavior_iti_df <- all_subs_g_dist %>% 
  select(subject, trial_numeric, trial_time) %>%
  filter(trial_time < 1) %>%
  mutate(trial_time = round(trial_time - 1, 2))

all_subs_dist <- full_join(all_subs_g_dist, behavior_iti_df)


```


```{r}

# load MNI data
mni_data <- read_csv(path(here(), "munge", "mni_coordinates_all_subs.csv"))

# create left/right pairs
leftright_data <- mni_data %>%
  mutate(left_right = if_else(X <= 0, "Left", "Right")) %>%
  select(subject, left_right, Electrode)


```


```{r merge-ieeg-hfa-data-behave-data}

mfg_hfa_clean_data <- mfg_hfa_data %>%
  mutate(freq = "hfa") %>%
  mutate(region = "MFG") %>%
  rename(power = theta) %>%
  mutate(electrode = gsub("_.*", "", electrode)) %>%
  mutate(first_elec = gsub("-.*", "", electrode)) %>%
  mutate(second_elec = gsub(".*-", "", electrode))  %>% 
  mutate(trial_time = trial_time - 3)  %>%
  filter(trial_time >= -1)


# merge with anatomy
mfg_hfa_clean_data <- left_join(mfg_hfa_clean_data, leftright_data, by = c("subject" = "subject", "first_elec" = "Electrode"))

# bind with behavioral data #
mfg_hfa_behave_df <- inner_join(all_subs_dist %>% select(-move_step) %>% mutate(trial_time = round(trial_time, 2)), 
                               mfg_hfa_clean_data %>% mutate(trial_time = round(trial_time, 2)))

# right only
mfgr_hfa_behave_df <- mfg_hfa_behave_df %>%
  filter(left_right == "Right")

```


```{r read-in-attack-tables}

## load and compile attack tables ##
for(sub in unique(all_subs_dist$subject)){
  
  tmp <- read_csv(path(here(), "data", "ieeg_behave", paste0(sub, "_attack_events.csv")))
  tmp <- tmp %>%
    mutate(subject = sub)
  
  if(exists("attack_events")){
    attack_events <- bind_rows(attack_events, tmp)
  } else {
    attack_events <- tmp
  }
  
}

## modify to get trials of interest ##
attack_events <- attack_events %>%
  mutate(trial_numeric = neural_trial_numeric + 1) %>%
  mutate(attacks_ids = paste0(subject, "_", trial_numeric))

attatck_events_coutn <- attack_events %>%
  filter(subject != "LL14" & subject != "BJH016")

mean(table(attatck_events_coutn$subject))
sd(table(attatck_events_coutn$subject))


```


```{r shift-to-attack}

# merge attack df
mfgr_attack_hfa_df <- left_join(mfgr_hfa_behave_df, attack_events %>% rename(attack_begin = event) %>% select(subject, trial_numeric, sample, attack_begin))
mfgr_attack_hfa_df <- mfgr_attack_hfa_df %>%
  mutate(attack_begin = if_else(is.na(attack_begin), 0, 1)) %>%
  group_by(subject, trial_numeric) %>%
  mutate(attacked = if_else(sum(attack_begin) != 0, 1, 0)) %>%
  ungroup()

# shift to center around turnaround  #
hfa_end_centered_df <- mfgr_attack_hfa_df %>%
  filter(attacked == 1) %>%
  # round time so that we can loop over time later
  mutate(trial_time = round(trial_time, 2)) %>%
  # filiter out ITI
  filter(reward_groups != 99 & !is.na(electrode)) %>%
  # prep electrode variables
  mutate(elec_id = paste0(subject, "_", gsub("_.*", "", electrode))) %>%
  # shift the time so that time 0 is the start of trial end
  group_by(elec_id, trial_numeric, subject, freq, region) %>%
  mutate(attack_time = if_else(attack_begin == 1, trial_time, -999)) %>%
  mutate(attack_time = max(attack_time)) %>%
  filter(attack_time > 0) %>%
  mutate(end_time = trial_time - trial_length) %>%
  mutate(end_time = round(end_time, 2)) %>%
  filter(trial_time >= attack_time -.5) %>%
  ungroup() 

behavior_check <- hfa_end_centered_df %>%
  select(subject, trial_numeric, sample, trial_time, attack_time, end_time, trial_length, died) %>%
  distinct()

```



```{r prep-chase, fig.height = 6, fig.width = 8}


chase_df <- hfa_end_centered_df %>%
  group_by(subject, trial_numeric) %>%
  mutate(chase_trial = any(Chase)) %>%
  filter(chase_trial == T & died == 0) %>%
  select(subject, trial_numeric, sample, trial_time, attack_time, end_time, trial_length, died, chase_trial, elec_id, power) %>%
  rowwise() %>%
  mutate(attack_length = trial_length - attack_time) %>%
  mutate(attack_end_time = -1* attack_length) %>%
  arrange(desc(attack_length)) %>%
  mutate(elec_trial_id = factor(paste0(elec_id, "_", trial_numeric)))


```


```{r prep-died, fig.height = 5, fig.width =6}


died_df <- hfa_end_centered_df %>%
  group_by(subject, trial_numeric) %>%
  mutate(chase_trial = any(Chase)) %>%
  filter(died == 1 & chase_trial == F) %>%
  mutate(min_time = max(end_time)) %>%
  filter(min_time == 0) %>%
  select(subject, trial_numeric, sample, trial_time, attack_time, end_time, trial_length, died, elec_id, power, min_time) %>%
  rowwise() %>%
  mutate(attack_length = trial_length - attack_time) %>%
  mutate(attack_end_time = -1* attack_length) %>%
  arrange(desc(attack_length)) %>%
  mutate(elec_trial_id = factor(paste0(elec_id, "_", trial_numeric)))
  


```

```{r rmfg-chase-died-stack, fig.height = 5, fig.width =10}

chase_died_df <- bind_rows(chase_df %>% mutate(case = "Chase trial"),
                           died_df %>% mutate(case = "Strike trial"))

chase_died_plot <- chase_died_df %>%
  ggplot(.,aes (x = end_time, y = elec_trial_id, color = power)) +
  geom_tile(aes(fill = power)) +
  geom_text(aes(x = attack_end_time), label = "*", size = 4, color = "white") +
  theme_minimal() +
  scale_fill_viridis_b(limits = c(-3, 3), oob = scales::squish, option = "C") +
  scale_color_viridis_b(limits = c(-3, 3), oob = scales::squish, option = "C")  +
  labs(x = "Time (s), locked to trial end", y = "rMFG Electrode and Trial stacks", fill = "Power (z)", color = "Power (z)") +
  theme(panel.background = element_rect(fill = "white"),
        legend.position = "right",
        panel.grid =  element_blank(),
        axis.text = element_text(family = "Gill Sans", color = "#2D2327", size = 8),
        axis.title = element_text(family = "Gill Sans", color = "#2D2327", size = 8),
        axis.text.y = element_blank(),
        legend.title = element_text(family = "Gill Sans", color = "#2D2327", size = 8),
        legend.text  = element_text(family = "Gill Sans", color = "#2D2327", size = 7),
        strip.text = element_text(family = "Gill Sans", color = "#2D2327", size = 8, face = 'bold'),
        plot.subtitle = element_text(family = "Gill Sans", color = "#2D2327", size = 7),
        plot.title = element_text(family = "Gill Sans", color = "#2D2327", size = 8, face = 'bold')) + 
  facet_wrap(~case, nrow = 1, scales = "free") +
  ggtitle("")

ggsave(path(here(), "figures", "attack", "figure5_chase_death_rmfg_plot.png"), 
       plot = chase_died_plot, 
       width = 4.1, height = 3, units = "in", dpi = 600)

```




```{r run-rmfg-attack*time-model}

# Set the number of cores for parallel processing
options(mc.cores = parallel::detectCores(), 
        brms.backend = "cmdstanr")  # Use cmdstanr for faster sampling

# set the priors #
priors <- c(
  prior(normal(0, 5), class = "Intercept"),            # Prior for the intercept
  prior(normal(0, 2), class = "b"),                    # Prior for fixed effects
  prior(exponential(1), class = "sd"),                 # Prior for random effects standard deviations
  prior(lkj(2), class = "cor")                         # Prior for random effects correlations
)


attack_duration_df <- hfa_end_centered_df %>%
  group_by(subject, trial_numeric) %>%
  filter(trial_time >= attack_time) %>%
  select(subject, trial_numeric, sample, trial_time, attack_time, end_time, trial_length, died, elec_id, distance_to_ghost, power) %>%
  rowwise() %>%
  mutate(attack_length = trial_length - attack_time) %>%
  mutate(attack_end_time = -1* attack_length) %>%
  ungroup() %>%
  arrange(desc(attack_length)) %>%
  mutate(elec_trial_id = factor(paste0(elec_id, "_", trial_numeric))) %>%
  mutate(distance_to_ghost_scaled = scale(distance_to_ghost)[,1]) %>%
  mutate(died = if_else(died == 1, "attack", "chase"))


# Fit the model
attack_died_hfa_model <- brm(
  formula = power ~ died*end_time + (1 + end_time | subject/elec_id),
  data = attack_duration_df,
  prior = priors,
  family = gaussian(),
  iter = 4000,
  warmup = 1000,
  chains = 4,
  control = list(adapt_delta = 0.99),
  seed = 1234
)


# save full model #
save(attack_died_hfa_model, file = path(here(), "results", "attack", "attack_rmfg_hfa_trial_time_model_brms.RData"))


load(path(here(), "results", "attack", "attack_rmfg_hfa_trial_time_model_brms.RData"))
summary(attack_died_hfa_model)

```
